---
title: "Final Project Preliminary"
date: 'November 15, 2020'
name: "Riya Mishra"
output: html_notebook
---
```{r}
library(DataComputing)
library(mosaic)
library(readr)
```

###Guiding Question 

In what ways can we improve the overall Happiness Score of a country? What are the top three predictors that determine the happiest country? Is there a particular region in the world that's happier than other regions? 


###Becoming Acquantied with the Data Sources 

##Uploading Process 
To attach my first dataset, I converted my .csv file to a .txt file and uploaded it onto the Stat184FinalProject notebook. Then, I clicked on Import Dataset in Environment and renamed the dataset from "2015" to "WorldHappiness". To make sure that the dataset was uploaded and saved, I ran the code "View(WorldHappiness)" and I successfully was able to view the dataset table. Next, I tried to extract certain variables to ensure that I can access and manipulate the dataset. 
```{r}
View(WorldHappiness)
WorldHappiness%>%
  select(Country, Region, Happiness.Rank)
```
For my next dataset, I used the HTML tables format since the dataset was embedded onto the site. I was successfully able to create a table after loading the dataset using read_html().

```{r}
library(rvest)
web_page <- "https://www.numbeo.com/crime/rankings_by_country.jsp?title=2015"
SetOfTables <- web_page %>%
  read_html() %>%
  html_nodes(css = "table") %>%
  html_table(fill = TRUE)
length(SetOfTables)

Table3 <- SetOfTables[[2]]
Table3
```
I tested to see if I can extract tables from the dataset. 
```{r}
Table3%>%
  select(Country, `Crime Index`, `Safety Index`)
```
## Where did you find them?

1. I found the World Happiness dataset through Kaggle. 
2. I found the Crime/Safety Index by Country dataset through a website called Numbeo. Numbeo is crowd-sourced global database of reported consumer prices, perceived crime rates, quality of health care, among other statistics.

##Who collected/maintains them?

1. The World Happiness is collected through a landmark survey from the Gallup World Poll. The report continues to gain global recognition as governments, organizations and civil society increasingly use happiness indicators to inform their policy-making decisions. 

2. The Crime/Safety Index by Country is collected and maintained by Numbeo itself. 

##When & Why were they originally collected?

1. The World Happines data started getting collected in 2012. The survey is collected by individuals who live in the country. They're asked to rate each question on a scale of 1 - 10. Once the data is collected, the Gallup World Poll creates an average value for each variable. It started to get collected as the United Nation started coming together and found that these surveys can help them laws and decision that will benefit their countries and to create awareness to authoritites about how their citizens feel. 

2. The Crime/Safety Index by Country  first started getting collected in 2012. The reason they started collecting this data is determine what countries are deemed more dangerous and which are deemed more safe and to find out what can be done to improve or maintain the scores.

##What does a case represent in each data source, and how many total cases are available?
1. World Happiness 

There are a total of 158 cases in this data set and each case represents the Happiness Rank of each country based off of various variables. 

```{r}
WorldHappiness
```
2. Crime Index by Country 2015
There are 147 cases in this dataset and each case represents the crime and safety index according to each country. There is a table for rank, however it is empty. If this table was completed, this data set would represent the ranking (from best to least) according to crime and safety index.
```{r}
Table3
```

## What are some of the variables that you plan to use
The variables I plan to use are basically all of them. However I do plan to remove Standard.Error and Dystopia Residual from the World Happiness data set as I don't think they are meaningful predictors in calculating overall happiness score. For the final project report, I plan to look more into it before I make a final decision. 


### Explore intuition related to the research question

## Create some informative plots and summary statistics 
```{r}
summary(WorldHappiness)
```
The highest Corruption score is 0.55 which is a lot higher than the mean 0.14. I'm interested to see which country is the most corrupt and from what region they are from. It also seems like the mean Generoisty index is more on the low end and the max is 0.795. I wonder what country has the highest generosity score is and what they are ranked. 
```{r}
summary(Table3)
```
The mean for both Crime and safety seem to be just a few numbers apart. However, a higher safety and a lower crime rate can probably lead to a better happiness score.
```{r}
MergedTable <-
  Table3%>%
  left_join(WorldHappiness, by = c("Country"))
MergedTable
```
```{r}
MergedTable%>% 
  ggplot(aes(x = Happiness.Score, y = `Crime Index`)) + geom_point()+geom_smooth(method = "lm", se =FALSE)
```
I was interested to see how big Crime plays in Happiness score. It is evident that a lower crime rate can lead to a higher happiness score. However, I'm intrigued by the one value that has a happiness score of about 7 but has the highest crime rate at about 80. 
```{r}
MergedTable%>% 
  ggplot(aes(x = Happiness.Score, y = `Safety Index`)) + geom_point()+geom_smooth(method = "lm", se =FALSE) + facet_wrap(~Region)
```
It seems like Eastern Asia is the safest area but doesn't seem like they have a wonderful Happiness score. 
```{r}
MergedTable%>% 
  ggplot(aes(x = Happiness.Score, y = Generosity)) + geom_point() + geom_smooth(method = "lm", se =FALSE)
```
There seems to be an upward trend in generosity. The nicer the people, the happier the country it seems like. 
## Describe preliminary observations and intuition about the research question

Looking at the statistics summary and the few graphs I made, I see that the median for Crime and Safety are about the same. A low Crime index is beneficial to the country and a higher Safety Index is better. I can see that there is a negative correlation between Crime Index and Happiness Score and a positive correaltion with the majority of the variables in respect to Happiness Score. I predict that Western European countries have the happiest countries in the World. I can also infer that Crime, Safety, and Economy will play a big role in Happiness Score. 
