---
title: "Final Project Report"
date: 'December 13, 2020'
name: "Riya Mishra"
output: html_notebook
---
```{r}
library(DataComputing)
library(mosaic)
library(readr)
```

###Guiding Question 

In what ways can we improve the overall Happiness Score of a country? What are the top three predictors that determine the happiest country? Is there a particular region in the world that's happier than other regions? 


###Data Access 

##Uploading Process 
To attach my first dataset, I converted my .csv file to a .txt file and uploaded it onto the Stat184FinalProject notebook. Then, I clicked on Import Dataset in Environment and renamed the dataset from "2015" to "WorldHappiness". To make sure that the dataset was uploaded and saved, I ran the code "View(WorldHappiness)" and I successfully was able to view the dataset table. Next, I tried to extract certain variables to ensure that I can access and manipulate the dataset. 
```{r}
View(WorldHappiness)
WorldHappiness%>%
  select(Country, Region, Happiness.Rank)
```
For my next dataset, I used the HTML tables format since the dataset was embedded onto the site. I was successfully able to create a table after loading the dataset using read_html().

```{r}
library(rvest)
web_page <- "https://www.numbeo.com/crime/rankings_by_country.jsp?title=2015"
SetOfTables <- web_page %>%
  read_html() %>%
  html_nodes(css = "table") %>%
  html_table(fill = TRUE)
length(SetOfTables)

CrimeandSafety <- SetOfTables[[2]]
CrimeandSafety
```
I tested to see if I can extract tables from the dataset. 
```{r}
CrimeandSafety%>%
  select(Country, `Crime Index`, `Safety Index`)
```
## Insepcting the Data
```{r} 
head(CrimeandSafety)
nrow(CrimeandSafety)
nrow(WorldHappiness)
names(WorldHappiness)
names(CrimeandSafety)
```

### Data Wrangling 

First, I'm going to merge the two datasets together so I can wrangle the data with both datasets as a whole. 
```{r}
MergedTable <-
  CrimeandSafety%>%
  left_join(WorldHappiness, by = c("Country"))
MergedTable
```
Next, I'm curious to know the average happiness score within all regions. 
```{r}

```


