---
name: 'Riya Mishra'
title: "Final Project Preliminary EDA"
date: 'November 15, 2020'
output: html_notebook
---


###Guiding Question 
What factor is the strongest predictor to determine the happiest country? 

To attach my dataset, I converted my .csv file to a .txt file and uploaded it onto the Stat184FinalProject notebook. Then, I clicked on Import Dataset in Environment and renamed the dataset from "2015" to "WorldHappiness". To make sure that the dataset is uploaded and saved, I ran the code "View(WorldHappiness)" and I successfully was able to view the dataset table. 

world happiness and see what countries are the happiest and what factors into them. 
Make a clear statement of a single guiding/research question that will drive your analysis.  It should be phrased as a question that you will try to investigate (i.e., it should have a question mark) 

```{r}
library(DataComputing)
library(mosaic)
library(readr)
```



```{r}
WorldHappiness%>%
  select(Country, Region, Happiness.Rank)
```
```{r}
library(rvest)
web_page <- "https://www.numbeo.com/crime/rankings_by_country.jsp?title=2015"
SetOfTables <- web_page %>%
  read_html() %>%
  html_nodes(css = "table") %>%
  html_table(fill = TRUE)
length(SetOfTables)

Table3 <- SetOfTables[[2]]
View(Table3)
```



```{r}
Table3%>%
  select(Country, `Crime Index`, `Safety Index`)
```





